Dryad Data Package for study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life

### 2022-07-06 dryad/README.Rmd
adding citations to dryad readme

---
title: 'README for Dryad Data Package from study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life"'
output:
  pdf_document:
      keep_md: yes
---

@@

	Corresponding Researcher
		name: Luna L. Sanchez Reyes
    institution: University of California, Merced, USA
    email: sanchez.reyes.luna@gmail.com

	Co-researcher 1
		name: Emily Jane McTavish
		institution: University of California, Merced, USA

	Co-researcher 2
		name: Brian C. O'Meara
		institution: University of Tennessee, Knoxville, USA

@@

@@

These data were generated to investigate and showcase the performance of the datelife R package (<https://github.com/phylotastic/datelife>).
We showcased the application of the package with one mock example and two different biological examples.
The mock example was GENERATED WITH
The first biological example uses datelife on a small sample of bird species.
The second one uses datelife on bird species belonging to the family Fringillidae of "true finches", following the NCBI taxonomy.
We investigate the performance of the package datelife with two analysis: a benchmarking analysis to measure computing time of functions, and a cross validation analysis to test the accuracy and precision of the functions.

>>>>

---
title: 'Dryad Data Package for study "DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life"'
output:
  pdf_document:
      keep_md: yes
---

@@

	Corresponding Researcher name: Luna L. Sanchez Reyes
  Corresponding Researcher institution: University of California, Merced, USA
  Corresponding Researcher email: sanchez.reyes.luna@gmail.com

	Co-researcher 1 name: Emily Jane McTavish
	Co-researcher 1	institution: University of California, Merced, USA

	Co-researcher 2 name: Brian C. O'Meara
	Co-researcher 2	institution: University of Tennessee, Knoxville, USA

@@

    Sánchez-Reyes LL, McTavish EJ & O’Meara BC. (2019). DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life. BioRxiv, 782094.

    Data from: DateLife: leveraging databases and analytical tools to reveal the dated Tree of Life. Dryad, Dataset

@@

These data were generated to investigate and showcase the performance of the datelife R package (<https://github.com/phylotastic/datelife>).
We showcased the application of the package with one mock example and two different biological examples.

The first biological example uses datelife on a small sample of bird species.
The second one uses datelife on bird species belonging to the family Fringillidae of "true finches", following the NCBI taxonomy.
The mock example was created by replacing species names from the small example with letters, and reducing the number of source chronograms.

We evaluated the performance of the package datelife with two analysis: a benchmarking analysis to measure computing time of functions, and a cross validation analysis to test the accuracy and precision of the functions.
